---
title: "Group 47 CA pollution burden"
author: "Narjes Mathlouthi & Julia Wilson"
date: "11/13/2021"
output: html_document
---


## Setup

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
library(here)
library(hexbin)

```


## Read in data

```{r, warning = FALSE, message = FALSE}

ces <- read_csv(here("data", "ces3demographics.csv")) %>% 
  clean_names()


```


## Visualize the data

```{r, warning = False, message = False}
ggplot(data = ces, 
       aes(x = white_percent, y = ces_3_0_score)) +
      geom_hex(bin = 5)+
  labs(x = "Percent of white population (%)",
       y = "CalEnviroScreen 3.0 score",
       title= "CalEnviroScreen 3.0 scores for white population",
      caption = "Calenviroscreen 3.0: A critical tool for achieving for advancing environmental justice (OEHHA). (2018)") + 
  scale_fill_gradient(low = "red2", high = "skyblue3", name = "Score results") +
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0), plot.title = element_text(hjust = 0.5))
```

**Figure1.**

From this figure, we can see that the percent of white population is low with high scores. CalEnviroScreen 3.0 scores and the percent of white population have a negative relationship with a negative downward slope. That means with higher percent of white population the score decreases.



#### Citation: 


Calenviroscreen 3.0: A critical tool for achieving for advancing environmental justice. Office of Environmental Health Hazard Assessment (OEHHA). (2018). Retrieved November 14, 2021, from https://calgreenzones.org/wp-content/uploads/2018/09/CEJA-CES-Report-2018_web.pdf. 

