---
title: "Group 47 CA pollution burden"
author: "Narjes Mathlouthi & Julia Wilson"
date: "11/13/2021"
output: html_document
---


#### Overview
This report analyzes pollution burdens based on on racial makeup of different areas from 2010 census data. 

**Data Citation:** 
California Office of Environmental Health Hazard Assessment. (2018). "CalEnviroScreen 3.0",         California Environmental Protection Agency.

## Setup

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
library(here)

#install.packages("hexbin")
library(hexbin)

```


## Read in data

```{r, warning = FALSE, message = FALSE}

ces <- read_csv(here("data", "ces3demographics.csv")) %>% 
  clean_names()


```


## Visualize the data

```{r , warning = FALSE, message = FALSE}
ggplot(data = ces, 
       aes(x = white_percent, y = ces_3_0_score)) +
      geom_hex() +
  labs(x = "White (%)",
       y = "Pollution Burden Score",
       title= "White Population Pollution Burden Score",
      caption = "CalEnviroScreen 3.0 A Tool For Advancing EnvironmentalJustice") + 
  scale_fill_gradient(low = "red2", high = "skyblue3") +
  theme_minimal()
```

**Figure 1:** This graph illustrates a negative correlation between the CalEnviroScreen pollution burden score and the percentage of white population. This supports the idea that white populations are protected from high exposure to environmental harm. 